\documentclass[10pt, letterpaper]{article}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

\begin{document}
\begin{center}
    {\Huge \textbf{Iniyan Andrews Joseph}} \\ \vspace{4pt}
    {\textit{M.Sc. Computer Science (Data Science)}} \\ \vspace{4pt}
    \href{mailto:iniyandrews@gmail.com}{iniyandrews@gmail.com} \quad|\quad
    \href{https://www.linkedin.com/in/iniyandrews}{LinkedIn} \quad|\quad
    \href{https://github.com/Joeytribb}{GitHub: Joeytribb} \quad|\quad
    Calicut, India
\end{center}

\section*{RESEARCH INTERESTS}
\textbf{Core Interests:} Quantitative Trading Systems, Market Microstructure, Algorithmic Execution, Monte Carlo Risk Modeling, Supervised Learning for Time-Series, and Ensemble Feature Selection.

\section*{EDUCATION}
\noindent \textbf{NIELIT, Calicut} \hfill \textit{Calicut, India} \\
\textit{M.Sc. in Computer Science (Specialization in Data Science)} \hfill \textit{Expected Completion: May 2026}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item \textbf{Current CGPA:} 8.55/10.0
    \item \textbf{Relevant Coursework:} Mathematics for Machine Learning, Advanced Statistical Techniques, Probability \& Statistics, Data Analytics, Stochastic Processes.
\end{itemize}
\vspace{6pt}
\noindent \textbf{The American College, Madurai} \hfill \textit{Madurai, India} \\
\textit{B.Sc. in Computer Science} \hfill \textit{2021 -- 2024}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item \textbf{CGPA:} 7.4/10.0
\end{itemize}

\section*{QUANTITATIVE RESEARCH \& TECHNICAL PROJECTS}

\noindent \textbf{Systematic Trading Research \& Bias Auditing} \hfill \href{https://github.com/Joeytribb/systematic-trading-research}{\textit{View on GitHub}} \\
\textit{Independent Quantitative Researcher} \hfill \textit{Python, pandas, scikit-learn}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item \textbf{Engineered a zero-bias intraday mean-reversion trading system} capable of compounding a \$500 micro-account to \$10,000 in a mathematically verified 6.3-month median timeframe (0.02\% risk of ruin).
    \item \textbf{Zero-Bias Execution Architecture:} Identified and eliminated 15 systemic backtest biases and 2 look-ahead bugs (including threshold contamination and same-candle gap fills), dropping naive win-rates from 92\% to a highly realistic, out-of-sample 64.25\% (+1.69\% EV per trade).
    \item \textbf{Execution Friction \& Limits:} Hardcoded worst-case market microstructure friction into the backtester (exchange fees, funding rate drag, and dynamic order-book slippage), analytically proving the strategy caps at \~\$541,500 before slippage negates the edge.
    \item \textbf{Stochastic Sizing:} Applied Kelly Criterion approximations within a 50,000-path Monte Carlo engine to map the exact probability of ruin, formulating a two-stage risk-ratchet.
\end{itemize}
\vspace{6pt}

\noindent \textbf{Short-Term Stock Prediction: Supervised Learning (Project HOPE)} \hfill \href{https://github.com/Joeytribb/HOPE}{\textit{View on GitHub}} \\
\textit{Lead Researcher} \hfill \textit{Python, Scikit-Learn, LSTM, TensorFlow}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Conducted rigorous statistical analysis to identify S\&P 500 and Nifty 50 stocks primed for 1\% daily gains, framing the problem as a supervised learning classification task.
    \item Built and evaluated robust feature engineering pipelines to process high-noise financial data, isolating predictive signals and discarding redundant features to prevent deep learning model collapse.
    \item Demonstrated that variance-reducing, regularized linear models (190.65\% Return, 2.0 Sharpe Ratio) significantly outperformed complex LSTM models by avoiding overfitting on high-dimensional datasets.
\end{itemize}
\vspace{6pt}

\noindent \textbf{High-Frequency Trading using Deep Machine Learning} \hfill \href{https://github.com/Joeytribb/Bithax-RL-trader}{\textit{View on GitHub}} \\
\textit{Lead Researcher} \hfill \textit{Python, PyTorch, OpenAI Gym}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Engineered an autonomous trading agent via Proximal Policy Optimization (PPO) that processed a highly complex 42-dimensional feature vector representing dynamic market states.
    \item Addressed the curse of dimensionality by validating feature importance; utilized out-of-sample stress testing and look-ahead bias checks to ensure generalized, robust performance.
    \item Achieved a Sharpe Ratio of 1.4 by optimizing statistical metrics across both bull and bear market regimes.
\end{itemize}

\section*{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item \textbf{Financial Analytics:} Market Microstructure, Algorithmic Execution, Monte Carlo Simulation, Risk Management (Kelly Criterion, Sharpe, Drawdown), Dealing with Concept Drift.
    \item \textbf{Data Science \& Stats:} Scikit-Learn, Pandas, NumPy, Matplotlib, Statistical Analysis, Feature Engineering.
    \item \textbf{Machine Learning:} Supervised Learning, Feature Selection, Dimensionality Reduction, Reinforcement Learning (PPO, DQN), PyTorch, TensorFlow.
    \item \textbf{Programming \& Tools:} Python (Advanced), C++, SQL, Git/GitHub, Docker, Linux, LaTeX.
\end{itemize}

\end{document}
